Tabular Constraint Learning

### 2016-05-10 Paper/ECAI/tabular.tex
Conclusion, removed discussion

@@

\section{Discussion and Conclusions}
\sergey{link to the github with implementations and the dataset}

\sergey{Future version, extensions, declarative stuff, bla-bla here}
discussion: what would be a language to extend the system, what would be the user interface? can it be used by community?  can it be complitely automated? interaction with user and highlighing?

conclusions 
% points: 1) can be a base for an actual plugin or a function in excel 2) novel problem and challenge for systems and constraint solvers 3) can be part of the complicated pipeline togehter with the header detection
Our goal was to automatically identify constraints that hold in a spreadsheet.
We have presented and evaluated an approach that is able to learn a large set of constraints from CSV data.

>>>>

\samuel{discussion: what would be a language to extend the system, what would be the user interface? can it be used by community?  can it be complitely automated? interaction with user and highlighing?
}

@@

\section{Conclusions}
\sergey{link to the github with implementations and the dataset}

\sergey{Future version, extensions, declarative stuff, bla-bla here}

conclusions 
% points: 1) can be a base for an actual plugin or a function in excel 2) novel problem and challenge for systems and constraint solvers 3) can be part of the complicated pipeline togehter with the header detection
Our goal was to automatically identify constraints that hold in a spreadsheet.
We have presented and evaluated an approach that is able to learn a large set of constraints from CSV data.
Moreover, the amount of redundant constraints found by the algorithm is limited despite the lack of more sophisticated post-processing steps.
